---
title: "Final_Project_EduSignal"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Reference

0. Job Market Signaling Game
1. Spence(1973), but ignore the section 6 about indices such as race or gender.
2. Course Tutorial(Video, E-book, Scripts, Slides)

## makecondition

```{r}
library(reticulate)
```

```{python}
from numpy.random import default_rng
from numpy import mean
import EduSignal
```

```{python}
Candidate = EduSignal.Candidate
Employer = EduSignal.Employer
JobMarket = EduSignal.JobMarket
```

### Reference Note

先從 Pooling Eqm 開始想，有點是在想 off-the-path 的部分如果沒問題，那麼 Separating Eqm 終究是成立了。

### Simple Spence

1. We assume the Wage_Schedule in Round1 is 1.4。

```{python Wage_Schedule_R1}
Wage_Schedule_R1 = 1.4
```

```{python SimpleSpence1}
SimpleSpence = JobMarket(employer = Employer(Low=1, High=2, Wage_Schedule=Wage_Schedule_R1),
                         candidate = Candidate(Group=1, Low=1, High=2, Wage_Schedule=Wage_Schedule_R1))
```

#### Go through candidate's class & instance method 

candidate's class method 
```{python SimpleSpence1_candidate}
SimpleSpence.candidate.__class__.Low
SimpleSpence.candidate.__class__.High
SimpleSpence.candidate.__class__.Wage_Schedule
SimpleSpence.candidate.__class__.candidate1toN #Only himself
SimpleSpence.candidate.Population(N=500)
SimpleSpence.candidate.__class__.candidate1toN[0:5] #500 candidates(first one is the main character)
len(SimpleSpence.candidate.__class__.candidate1toN) #500
SimpleSpence.candidate.q1()
SimpleSpence.candidate.__class__.q1 
SimpleSpence.candidate.Uniform_Payoff() #q1*1+(1-q1)*2 = 2-q1
SimpleSpence.candidate.__class__.Uniform_Payoff
```

candidate's instance method 
```{python}
SimpleSpence.candidate.Group
SimpleSpence.candidate.__class__.Wage_Schedule
SimpleSpence.candidate.Signaling_Cost(Education=SimpleSpence.candidate.__class__.Wage_Schedule) #Group1 = 1.4/1
SimpleSpence.candidate.Optimal_Education() #Uniform_Payoff-1.4 v.s. 1-0
SimpleSpence.candidate.Signal
```

#### Go through employer's instance method 

```{python SimpleSpence1_employer}
SimpleSpence.employer.High
SimpleSpence.employer.Low
SimpleSpence.employer.Wage_Schedule
SimpleSpence.employer.Possible_Wage(SimpleSpence.candidate.Signal)
```

#### Go through the Eqm methods

Start with the Pooling_Eqm method can be more handy since we want to avoid it.
```{python SimpleSpence1_Pooling_Eqm}
SimpleSpence.Pooling_Eqm()
```

```{python SimpleSpence1_Separating_Eqm}
SimpleSpence.Separating_Eqm()
```

### Round 1.1: Check if the candidate is from the another group

不再造一個 candidate(instance)，因為 `Candidate.candidate1toN.append(self)` 會讓 `len(SimpleSpence.candidate.__class__.candidate1toN)` 從 500 變成 501，但是已經生成好的 class variable，包含 q1 和 Uniform_Payoff 都是由 500 人下去算的。
```{python}
# SimpleSpence = JobMarket(employer = Employer(Low=1, High=2, Wage_Schedule=1.4),
#                          candidate = Candidate(Group=1, Low=1, High=2, Wage_Schedule=1.4))
```

所以選擇單方面改`SimpleSpence.candidate.Group`，即是改`SimpleSpence.candidate.__class__.candidate1toN[0]`，也就是改該 candidate(instance) 的 Group。但還是有點不完全貼近現實。
```{python SimpleSpence1.1_candidate}
# SimpleSpence.candidate.Group #1
# SimpleSpence.candidate.Population()
# SimpleSpence.candidate.q1()
SimpleSpence.candidate.Group = 2
SimpleSpence.candidate.__class__.candidate1toN[0:5]
len(SimpleSpence.candidate.__class__.candidate1toN) #Remain 500

SimpleSpence.candidate.__class__.Wage_Schedule
SimpleSpence.candidate.__class__.q1
SimpleSpence.candidate.__class__.Uniform_Payoff
SimpleSpence.candidate.Signaling_Cost(Education=SimpleSpence.candidate.__class__.Wage_Schedule) #1.4/2
SimpleSpence.candidate.Optimal_Education() #Uniform_Payoff-0 v.s 2-1.4/2
SimpleSpence.candidate.Signal
```

```{python SimpleSpence1.1_employer}
SimpleSpence.employer.High
SimpleSpence.employer.Low
SimpleSpence.employer.Wage_Schedule
SimpleSpence.employer.Possible_Wage(SimpleSpence.candidate.Signal)
```

```{python SimpleSpence1.1_Separating_Eqm}
SimpleSpence.candidate.Group
SimpleSpence.candidate.Signal
SimpleSpence.Separating_Eqm()
```

```{python SimpleSpence1.1_Pooling_Eqm}
SimpleSpence.Pooling_Eqm()
```

## Round2: Change the Wage_Schedule

```{python Wage_Schedule_R2}
Wage_Schedule_R2 = 0.9
```

理由同 Round 1.1
```{python}
# SimpleSpence = JobMarket(employer = Employer(Low=1, High=2, Wage_Schedule=Wage_Schedule_R2),
#                          candidate = Candidate(Group=1, Low=1, High=2, Wage_Schedule=Wage_Schedule_R2))
```

市場環境改變了
```{python}
SimpleSpence.candidate.__class__.Wage_Schedule = Wage_Schedule_R2
SimpleSpence.employer.Wage_Schedule = Wage_Schedule_R2
```

#### Go through candidate's class & instance method 

candidate's class method 
```{python SimpleSpence2_candidate}
# The class method are fixed as round1
# SimpleSpence.candidate.Population()
# SimpleSpence.candidate.q1() 
# SimpleSpence.candidate.Uniform_Payoff()
SimpleSpence.candidate.__class__.Low
SimpleSpence.candidate.__class__.High
SimpleSpence.candidate.__class__.Wage_Schedule
SimpleSpence.candidate.__class__.candidate1toN[0:5]
SimpleSpence.candidate.__class__.q1 
SimpleSpence.candidate.__class__.Uniform_Payoff
```

candidate's instance method 
```{python}
SimpleSpence.candidate.Group = 1 #Convert back to 1 after Round 1.1
SimpleSpence.candidate.__class__.Wage_Schedule
SimpleSpence.candidate.Signaling_Cost(Education=SimpleSpence.candidate.__class__.Wage_Schedule) #0.9/1
SimpleSpence.candidate.Optimal_Education() #Uniform_Payoff-0.9 v.s. 1-0
SimpleSpence.candidate.Signal
```

#### Go through employer's instance method 

```{python SimpleSpence2_employer}
SimpleSpence.employer.High
SimpleSpence.employer.Low
SimpleSpence.employer.Wage_Schedule
SimpleSpence.employer.Possible_Wage(SimpleSpence.candidate.Signal)
```

#### Go through instance Eqm methods again

Start with the Pooling_Eqm method can be more handy since we want to avoid it.
```{python SimpleSpence2_Pooling_Eqm}
SimpleSpence.Pooling_Eqm()
```

```{python SimpleSpence2_Separating_Eqm}
SimpleSpence.Separating_Eqm()
```

### Round 2.1: Check if the candidate is from the another group

```{python SimpleSpence2.1_candidate}
#Round1.1 = Group2, Round2 = Group1...
# SimpleSpence.candidate.Population() #No need to arouse again
# SimpleSpence.candidate.q1() #No need to arouse again

SimpleSpence.candidate.Group = 2 
SimpleSpence.candidate.__class__.candidate1toN[0:5]
SimpleSpence.candidate.__class__.Wage_Schedule
SimpleSpence.candidate.__class__.q1
SimpleSpence.candidate.__class__.Uniform_Payoff
SimpleSpence.candidate.Signaling_Cost(Education=SimpleSpence.candidate.__class__.Wage_Schedule) #0.9/2
SimpleSpence.candidate.Optimal_Education() #Uniform_Payoff-0 v.s 2-0.9/2
SimpleSpence.candidate.Signal
```

```{python SimpleSpence2.1_employer}
SimpleSpence.employer.High
SimpleSpence.employer.Low
SimpleSpence.employer.Wage_Schedule
SimpleSpence.employer.Possible_Wage(SimpleSpence.candidate.Signal)
```

```{python SimpleSpence2.1_Separating_Eqm}
SimpleSpence.candidate.Group
SimpleSpence.candidate.Signal
SimpleSpence.Separating_Eqm()
```

```{python SimpleSpence2.1_Pooling_Eqm}
SimpleSpence.Pooling_Eqm()
```

### Self-Reflection

0. Candidate class methods for Population, q1(Group1 proportion), Uniform_Payoff。

1. q1 是否真的能看到？那真要想，多少算合理？求職平台怎麼降低這個不對稱（對於雇主和求職者都是）e.g. 多少人看過這個職缺＋錄取經驗分享？

2.（N=500），Low、High、Wage_Schedule 的懸殊感。

3. Signaling_Cost = Education/Group。有 Group1 和 Group 2，但是他們的生產力效率可以不見得是 1:2。(1:1/2)

    - 可以是 1:5 甚至是 1:10 之類的。表達（庸才, 人才），（庸才，將才），（庸才，將將之才）的差別。
    
        - Cost of Group1: a1*y = (1) * y
        
        - Cost of Group2: a2*y = (1/5) * y
    
自然也會影響到人才會有意願 Signaling 的可能性。When Group2 will be better-off with signal. 

$$
q1 > \frac{a2}{a1}
$$




